---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GSPglass

<!-- badges: start -->
<!-- badges: end -->

GSPglass is an interactive Shiny app that scrapes, summarizes, and topic models Glassdoor reviews. Install the package, run the app, and follow the directions provided. 

## Installation

You can install the development version of GSPglass from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("taylorgrant/GSPglass")
```

## Example

To call the Shiny app, do as follows:

```{r, eval = FALSE}
library(GSPglass)
runApp()
```

The modal pop-up explains everything. Additional information about the topic modeling process can be found in the About section of the app.

A standardized rmarkdown report is included in the app. After topic modeling, the user may choose to generate the report. 
