---
title: "Glassdoor Reviews: `r params$data$name`"
output: 
  html_document:
    theme: flatly
params:
  data: data
---

<style>
body {
    position: absolute;
    left: 20px;}

.main-container {
  max-width: 90% !important;
  margin: auto;
}
</style>

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri(system.file('rmd', "gsp_logo_lumen.png", package = "GSPglass")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:8px;')
```

```{r, setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE, # Default: TRUE
  include = TRUE, # Default: TRUE
  warning = FALSE, 
  message = FALSE)

# load packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, highcharter, DT, rmarkdown)
data <- params$data
fulldata <- data$pros$df |>
          dplyr::select(review_date:model_topic) |>
          dplyr::rename(pro_topic = model_topic) |>
          dplyr::left_join(dplyr::select(data$cons$df, c(doc_id, con_topic = model_topic))) |> 
  dplyr::rename(pros = text)

year_avg <- fulldata |> 
  dplyr::mutate(year = lubridate::year(review_date)) |> 
  dplyr::group_by(year) |> 
  dplyr::summarise(avg = mean(rating, na.rm = TRUE))
```


## {.tabset .tabset-pills}

### About

#### What is this?
This is a pull of **`r nrow(fulldata)`** Glassdoor reviews for **`r data$name`**. These are all of the reviews available on Glassdoor and they cover a time frame of **`r range(fulldata$review_date)[1]`** to **`r range(fulldata$review_date)[2]`**. The average rating for **`r data$name`** is **`r round(mean(fulldata$rating, na.rm = TRUE), 1)`**.

---

#### What is in a Glassdoor review? 
Glassdoor reviewers can provide information as to their role within the company, whether they are current or former employees, the duration of their employement, as well as their rating of the company (low of 1 to a high of 5). In addition, reviewers provide a summary blurb and Pros and Cons of their time at the company. To make the digestion and interpretation of these reviews easier, both positive and negative reviews have been topic modeled (to learn more about topic modeling, see the **Notes** tab).  

Simply click on the tabs above to navigate through this document. Below is a quick description of what will be found. 

  - **Summary Data:** Provides some basic data about reviews by company and over time
  - **Topic Modeling:** Modeling the Pros and Cons separately. Topics are placed on a 2-dimensional scaling for ease of interpretion. The top terms for each topic are found in the "Top Terms per Topic" tab. "Topics by Company" breaks out the percentage of each companies reviews that fall into each topic
  - **Full Table:** All reviews with the Pro and Con topic assigned to each. This table is fully filterable and searchable. In addition, the table can be downloaded by pressing the Excel button in the upper left

### Summary Data {.tabset .tabset-pills}

#### Average Rating 

There is `r ifelse(confint(lm(rating ~ 1, data = subset(fulldata, status == 'Current Employee')))[1] > confint(lm(rating ~ 1, data = subset(fulldata, status == 'Former Employee')))[2], "**a significant**", "an insignificant")` ratings gap of **`r round(mean(fulldata[fulldata$status == "Current Employee",]$rating),1) - round(mean(fulldata[fulldata$status == "Former Employee",]$rating),1)`** points between Former and Current employees of **`r data$name`**. 

---

```{r, summary-table}
fulldata |> 
  summarise(n = n(),
            mean = mean(rating),
            sd = sd(rating)) |>  
  mutate(margin = qt(0.975, df = n-1)*sd/sqrt(n),
         low = round(mean - margin, 1), 
         high = round(mean + margin, 1)) |>  
  mutate(avg = glue::glue("{round(mean,1)} [{low} - {high}]"),
         status = "All Employees") |>  
  select(status, avg, n) |> 
  bind_rows(fulldata |> 
  group_by(status) |>
  summarise(n = n(),
            mean = mean(rating),
            sd = sd(rating)) |>  
  mutate(margin = qt(0.975, df = n-1)*sd/sqrt(n),
         low = round(mean - margin, 1), 
         high = round(mean + margin, 1)) |>  
  mutate(avg = glue::glue("{round(mean,1)} [{low} - {high}]")) |> 
  select(status, avg, n)) |> 
  datatable(
    colnames = c("Status", "Average Rating [95% CI]", "Review Count"),
            rownames = FALSE,
            options = list(dom = "t",
                           buttons = c('excel'),
                           pageLength = 3,
            columnDefs = list(list(className = "dt-right", targets = 1))),
                caption = "Summary Statistics by Employment Status") 

```

#### Ratings over time

As can be seen below, for the current year, the average employee rating for **`r data$name`** is **`r round(year_avg[year_avg$year == lubridate::year(Sys.Date()),]$avg,1)`** which is `r ifelse(year_avg[year_avg$year == lubridate::year(Sys.Date()),]$avg > year_avg[year_avg$year == lubridate::year(Sys.Date())-1,]$avg, "**greater**", "**less**")` than last year. 

---

```{r}
tmpdata <- fulldata |>  
  mutate(year = lubridate::year(review_date)) |>  
  group_by(year) |>  
  summarise(n = n(), 
            avg = round(mean(rating),1))

highcharter::highchart() |>
    highcharter::hc_yAxis_multiples(
      list(title = list(text = "Review Count")),
      list(title = list(text = "Average Rating"),
           max = 5, opposite = TRUE)
    ) |>
    highcharter::hc_xAxis(title = list(text = glue::glue("Year")),
                          type = "category") |>
    highcharter::hc_add_series(data = tmpdata, "column",
                               highcharter::hcaes(x = year, y = n),
                  name = "Review Count", yAxis = 0) |>
    highcharter::hc_add_series(data = tmpdata, "line",
                               highcharter::hcaes(x = year, y = avg),
                  name = "Average Rating", yAxis = 1) |>
    highcharter::hc_tooltip(shared = TRUE) |>
    highcharter::hc_title(
      text = glue::glue("Summary of Reviews for {data$name}"),
      align = "left"
    ) |>
    highcharter::hc_subtitle(
      text = glue::glue("By Year"),
      align = "left"
    ) |>
    highcharter::hc_exporting(enabled = TRUE)
```

#### Wordcloud - Pros

```{r}
tmpdat <- data$pros$df |>
    dplyr::pull(text) |>
    purrr::map(stringr::str_to_lower) |>
    stringr::str_split("\\s+") |>
    unlist() |>
    tibble::tibble() |>
    purrr::set_names("word") |>
    dplyr::mutate(word = gsub("(?!\\')[[:punct:]]", " ", word, perl=TRUE)) |>
    dplyr::count(word, sort = TRUE) |>
    dplyr::anti_join(tidytext::stop_words, by = "word") |>
    utils::head(80)

  highcharter::hchart(tmpdat, "wordcloud", highcharter::hcaes(name = word, weight = log(n))) |>
    highcharter::hc_tooltip(
      useHTML = TRUE,
      table = FALSE,
      headerFormat = "",
      pointFormat = "<span style=\"color:{series.color}\">\u25CF</span> <b>Word Count</b><br>{point.word}: {point.n}<br>"
    ) |>
    highcharter::hc_title(text = glue::glue("Glassdoor - Pros Wordcloud"),
                          align = "left") |>
    highcharter::hc_caption(
      text = glue::glue("<em>Top 80 terms used with stop words removed. Based on {nrow(data$pros$df)} total reviews of {data$name}.</em>")
    ) |> 
    hc_size(width = 800) |> 
  highcharter::hc_exporting(enabled = TRUE)
```

#### Wordcloud - Cons

```{r}
tmpdat <- data$cons$df |>
    dplyr::pull(text) |>
    purrr::map(stringr::str_to_lower) |>
    stringr::str_split("\\s+") |>
    unlist() |>
    tibble::tibble() |>
    purrr::set_names("word") |>
    dplyr::mutate(word = gsub("(?!\\')[[:punct:]]", " ", word, perl=TRUE)) |>
    dplyr::count(word, sort = TRUE) |>
    dplyr::anti_join(tidytext::stop_words, by = "word") |>
    utils::head(80)

  highcharter::hchart(tmpdat, "wordcloud", highcharter::hcaes(name = word, weight = log(n))) |>
    highcharter::hc_tooltip(
      useHTML = TRUE,
      table = FALSE,
      headerFormat = "",
      pointFormat = "<span style=\"color:{series.color}\">\u25CF</span> <b>Word Count</b><br>{point.word}: {point.n}<br>"
    ) |>
    highcharter::hc_title(text = glue::glue("Glassdoor - Cons Wordcloud"),
                          align = "left") |>
    highcharter::hc_caption(
      text = glue::glue("<em>Top 80 terms used with stop words removed. Based on {nrow(data$cons$df)} total reviews of {data$name}.</em>")
    ) |> 
    hc_size(width = 800) |> 
  highcharter::hc_exporting(enabled = TRUE)
```

### Topic Modeling - Pros {.tabset .tabset-pills}

#### Topic Plot

When describing the positives about **`r data$name`**, reviewers discussed a total of **`r nrow(data$pros$fulldata)`** topics. The most frequently raised of these topics accounted for **`r data$pros$fulldata$pct[1]`** of positive reviews.

---

```{r}
# set up tooltip
  # ct <- nrow(dat$fulldata)
  x <- paste0("Term ", 1:12, ":")
  y <- sprintf("{point.%s} ", paste0("t_", 1:12))
  tltip <- highcharter::tooltip_table(x, y)

  # topic nouns
  data$pros$fulldata$topic_nouns <- gsub("((?:[^,]+, ){2}[^,]+),", "\\1<br>", data$pros$fulldata$topic_nouns)
  highcharter::hchart(
    data$pros$fulldata,
    "scatter",
    highcharter::hcaes(x, y, name = Topic, size = frac, group = Topic, label = Topic
    ),
    showInLegend = FALSE,
    dataLabels = list(
      enabled = TRUE,
      format = "{point.newid}"
    ),
    minSize = 20,
    maxSize = 70
  ) |>
    highcharter::hc_xAxis(
      title = list(text = "PCA 1"),
      max = data$pros$range[2],
      min = data$pros$range[1],
      gridLineWidth = 0,
      lineWidth = 0,
      tickWidth = 0,
      plotLines = list(list(
        value = 0,
        color = '#A9A9A9',
        dashStyle = 'solid',
        width = 1,
        zIndex = 1))
    ) |>
    highcharter::hc_yAxis(
      title = list(text = "PCA 2"),
      max = data$pros$range[2],
      min = data$pros$range[1],
      gridLineWidth = 0,
      plotLines = list(list(
        value = 0,
        color = "#A9A9A9",
        dashStyle = "solid",
        width = 1
      ))
    ) |>
    highcharter::hc_title(
      text = glue::glue("Intertopic Distance Map - {data$name}"),
      align = "left"
    ) |>
    highcharter::hc_subtitle(
      text = glue::glue("Estimated Topics for Positive Reviews"),
      align = "left"
    ) |>
    highcharter::hc_caption(
      text = glue::glue("<b>Mouse over each point to see the topic size and top terms associated with that topic. The score for each word is based upon an optimal blend of topic-specific probability and relevance.</b><br><em>Points are plotted such that they represent 2-dimensional scalings of our topic model. The location of each topic within the two dimensions is informative - the closer a topic is to another, the more similar the topics (and vice versa). The size of each bubble indicates the size of the topic relative to others. The number of topics has been selected via coherence scoring; in this case {nrow(data$pros$fulldata)} topics is the ideal.</em>")
    ) |>
    highcharter::hc_tooltip(
      useHTML = TRUE,
      table = FALSE,
      headerFormat = "<span style=\"color:{series.color}\">\u25CF</span> <b>{point.key}</b><br><span style=\"color:{series.color}\">\u25CF</span> <b>{point.point.topic_nouns}</b> (Size: {point.point.pct}) <br><br> <b> Term #: Word (Score)</b> ",
      pointFormat = tltip
    ) |>
    hc_size(width = 800, height = 800) |> 
  highcharter::hc_exporting(enabled = TRUE)
```

#### Top Terms per Topic 

The table below simply converts the Topic Plot data into a flat table. 

---

```{r}
nms <- c("Topic", "Topic Size", paste("Term", 1:12))

data$pros$fulldata$topic_nouns <- stringr::str_replace_all(data$pros$fulldata$topic_nouns, "<br>", ",")
data$pros$fulldata  |>
    dplyr::mutate(topic = paste0(Topic,": ", topic_nouns)) |>
    dplyr::select(topic, `Topic Size` = pct, dplyr::starts_with("t_")) |>
    purrr::set_names(nms) |>
    tidyr::pivot_longer(names_to = "Term",
                 values_to = "Score",
                 -c("Topic", "Topic Size")) |>
    dplyr::select(-c(`Topic Size`)) |>
    tidyr::pivot_wider(names_from = Topic,
                values_from = c(Score)) |>
    DT::datatable(rownames = FALSE,
                  options = list(dom = "Blrtip",
                                 pageLength = 12,
                                 buttons = c('excel'),
                                 scrollX = TRUE),
                  caption = glue::glue("Top terms per Positive topic"))
```

#### Positive Topics by Year

```{r}
tmpdat <- data$pros$df |>
    dplyr::mutate(year = lubridate::year(review_date)) |>
    dplyr::count(year, model_topic) |>
    dplyr::group_by(year) |>
    dplyr::mutate(pct = n/sum(n)) |>
    dplyr::filter(!is.na(model_topic)) |> 
  dplyr::left_join(dplyr::select(data$pros$fulldata, c(newid, topic_nouns)),
                   by = c("model_topic" = "newid")) |> 
  dplyr::mutate(topic_nouns = gsub("((?:[^,]+, ){2}[^,]+),", "\\1<br>", topic_nouns))

  highcharter::hchart(tmpdat, 'column',
                      highcharter::hcaes(x = year, y = round(pct*100, 1), group = model_topic)) |>
    highcharter::hc_plotOptions(column = list(
      dataLabels = list(enabled = FALSE),
      stacking = "normal")
    ) |>
    highcharter::hc_xAxis(title = list(text = glue::glue("Year")),
                          type = "category") |>
    highcharter::hc_yAxis(title = list(text = glue::glue("Percentage")),
                          max = 100
                          ) |>
    highcharter::hc_title(text = glue::glue("Topic volume by year: {data$name}"),
                          align = "left") |> 
    highcharter::hc_tooltip(
      useHTML = TRUE,
      table = FALSE,
      headerFormat = "<b>{point.x}</b>",
      pointFormat = "<br><span style=\"color:{series.color}\">\u25CF</span> <b>Topic: {point.model_topic}</b><br>
      <span style=\"color:{series.color}\">\u25CF</span> <b>Terms:</b> {point.topic_nouns}<br>
      <span style=\"color:{series.color}\">\u25CF</span> <b>Count:</b> {point.n} ({point.y}%)<br>"
    ) |> 
    hc_size(width = 800) |> 
  highcharter::hc_exporting(enabled = TRUE)
```

### Topic Modeling - Cons {.tabset .tabset-pills}

#### Topic Plot

When describing the positives about **`r data$name`**, reviewers discussed a total of **`r nrow(data$cons$fulldata)`** topics. The most frequently raised of these topics accounted for **`r data$cons$fulldata$pct[1]`** of positive reviews.

---

```{r}
# set up tooltip
  # ct <- nrow(dat$fulldata)
  x <- paste0("Term ", 1:12, ":")
  y <- sprintf("{point.%s} ", paste0("t_", 1:12))
  tltip <- highcharter::tooltip_table(x, y)

  # topic nouns
  data$cons$fulldata$topic_nouns <- gsub("((?:[^,]+, ){2}[^,]+),", "\\1<br>", data$cons$fulldata$topic_nouns)
  highcharter::hchart(
    data$cons$fulldata,
    "scatter",
    highcharter::hcaes(x, y, name = Topic, size = frac, group = Topic, label = Topic
    ),
    showInLegend = FALSE,
    dataLabels = list(
      enabled = TRUE,
      format = "{point.newid}"
    ),
    minSize = 20,
    maxSize = 70
  ) |>
    highcharter::hc_xAxis(
      title = list(text = "PCA 1"),
      max = data$cons$range[2],
      min = data$cons$range[1],
      gridLineWidth = 0,
      lineWidth = 0,
      tickWidth = 0,
      plotLines = list(list(
        value = 0,
        color = '#A9A9A9',
        dashStyle = 'solid',
        width = 1,
        zIndex = 1))
    ) |>
    highcharter::hc_yAxis(
      title = list(text = "PCA 2"),
      max = data$cons$range[2],
      min = data$cons$range[1],
      gridLineWidth = 0,
      plotLines = list(list(
        value = 0,
        color = "#A9A9A9",
        dashStyle = "solid",
        width = 1
      ))
    ) |>
    highcharter::hc_title(
      text = glue::glue("Intertopic Distance Map - {data$name}"),
      align = "left"
    ) |>
    highcharter::hc_subtitle(
      text = glue::glue("Estimated Topics for Negative Reviews"),
      align = "left"
    ) |>
    highcharter::hc_caption(
      text = glue::glue("<b>Mouse over each point to see the topic size and top terms associated with that topic. The score for each word is based upon an optimal blend of topic-specific probability and relevance.</b><br><em>Points are plotted such that they represent 2-dimensional scalings of our topic model. The location of each topic within the two dimensions is informative - the closer a topic is to another, the more similar the topics (and vice versa). The size of each bubble indicates the size of the topic relative to others. The number of topics has been selected via coherence scoring; in this case {nrow(data$cons$fulldata)} topics is the ideal.</em>")
    ) |>
    highcharter::hc_tooltip(
      useHTML = TRUE,
      table = FALSE,
      headerFormat = "<span style=\"color:{series.color}\">\u25CF</span> <b>{point.key}</b><br><span style=\"color:{series.color}\">\u25CF</span> <b>{point.point.topic_nouns}</b> (Size: {point.point.pct}) <br><br> <b> Term #: Word (Score)</b> ",
      pointFormat = tltip
    ) |>
    hc_size(width = 800, height = 800) %>%
  highcharter::hc_exporting(enabled = TRUE)
```

#### Top Terms per Topic 

The table below simply converts the Topic Plot data into a flat table. 

---

```{r}
nms <- c("Topic", "Topic Size", paste("Term", 1:12))

data$cons$fulldata$topic_nouns <- stringr::str_replace_all(data$cons$fulldata$topic_nouns, "<br>", ",")
data$cons$fulldata  |>
    dplyr::mutate(topic = paste0(Topic,": ", topic_nouns)) |>
    dplyr::select(topic, `Topic Size` = pct, dplyr::starts_with("t_")) |>
    purrr::set_names(nms) |>
    tidyr::pivot_longer(names_to = "Term",
                 values_to = "Score",
                 -c("Topic", "Topic Size")) |>
    dplyr::select(-c(`Topic Size`)) |>
    tidyr::pivot_wider(names_from = Topic,
                values_from = c(Score)) |>
    DT::datatable(rownames = FALSE,
                  options = list(dom = "Blrtip",
                                 pageLength = 12,
                                 buttons = c('excel'),
                                 scrollX = TRUE),
                  caption = glue::glue("Top terms per Negative topic"))
```

#### Negative Topics by Year

```{r}
tmpdat <- data$cons$df |>
    dplyr::mutate(year = lubridate::year(review_date)) |>
    dplyr::count(year, model_topic) |>
    dplyr::group_by(year) |>
    dplyr::mutate(pct = n/sum(n)) |>
    dplyr::filter(!is.na(model_topic)) |> 
  dplyr::left_join(dplyr::select(data$cons$fulldata, c(newid, topic_nouns)),
                   by = c("model_topic" = "newid")) |> 
  dplyr::mutate(topic_nouns = gsub("((?:[^,]+, ){2}[^,]+),", "\\1<br>", topic_nouns))

  highcharter::hchart(tmpdat, 'column',
                      highcharter::hcaes(x = year, y = round(pct*100, 1), group = model_topic)) |>
    highcharter::hc_plotOptions(column = list(
      dataLabels = list(enabled = FALSE),
      stacking = "normal")
    ) |>
    highcharter::hc_xAxis(title = list(text = glue::glue("Year")),
                          type = "category") |>
    highcharter::hc_yAxis(title = list(text = glue::glue("Percentage")),
                          max = 100
                          ) |>
    highcharter::hc_title(text = glue::glue("Topic volume by year: {data$name}"),
                          align = "left") |> 
    highcharter::hc_tooltip(
      useHTML = TRUE,
      table = FALSE,
      headerFormat = "<b>{point.x}</b>",
      pointFormat = "<br><span style=\"color:{series.color}\">\u25CF</span> <b>Topic: {point.model_topic}</b><br>
      <span style=\"color:{series.color}\">\u25CF</span> <b>Terms:</b> {point.topic_nouns}<br>
      <span style=\"color:{series.color}\">\u25CF</span> <b>Count:</b> {point.n} ({point.y}%)<br>"
    ) |> 
    hc_size(width = 800) |> 
  highcharter::hc_exporting(enabled = TRUE)
```

### Full Table 

```{r}
DT::datatable(fulldata,
              colnames = c("Review Date", "Job Title", "Employment Status",
                           "Employment Duration", "Summary", "Rating",
                           "Pros", "Cons", "doc_id", "Pros: Topic", "Cons: Topic"),
              extensions = "Buttons",
              filter = list(position = "top", clear = FALSE),
              rownames = FALSE,
              options = list(
                # searching = FALSE,
                dom = "Blftp",
                buttons = c('excel'),
                columnDefs = list(list(width = '300px', targets = c(6,7,8)),
                                  list(visible = FALSE, targets = c("doc_id")))),
              caption = "All reviews")
```

### Notes

#### About Topic Modeling:
Topic modeling is an unsupervised dimension reduction method that is commonly used when trying to summarize large volumes of text. In this case, we are
leveraging the BTM model, which uses 'word-word co-occurrence patterns' (e.g., biterms) within the
texts. The BTM model excels at finding topics in shorter texts such as survey responses, tweets, and online reviews.
For more detail, the reference paper for the model can be found [here](https://github.com/xiaohuiyan/xiaohuiyan.github.io/blob/master/paper/BTM-WWW13.pdf).<br><br>
To properly model the text, all reviews are tagged by their appropriate parts of speech. To do this, we leverage a pre-trained annotator model to
tokenize, tag, and parse each word. This model also captures the co-occurrence frequency of all nouns, verbs, and adjectives within 3 skips
of each term within each review text. This data is then passed into our BTM model. The BTM algorithm next
estimates a model for varying number of topics - 5 to 15 topics - and selects the best one based on each model's coherence
score.<br><br>When the best model is identified, the topics are then plotted into a 2-dimensional space via the methodology outlined
[here](https://aclanthology.org/W14-3110.pdf). The distance between topics in
this visualization is meaningful - the closer the topics, the more similar they are. 
The bubble size indicates the size of the topic relative to others; mousing over each bubble will provide the top adjective and 4-5 nouns, which serve as a crude descriptor of the topic. Additional data provided includes the proportion of the topic and the top 12 most relevant and salient terms for that topic.
Because Pros and Cons are separate texts, each is modeled and visualized separately.
<br><br>Because the modeling process is unsupervised, there is no north star as to the correct number of topics. Some may potentially overlap, or seem redundant. Take the time to read through the reviews for specific topics to see how consistent the overlap may be. This is meant as a quick way to summarize reviews, so use it as an aid, but interpretation of the output, as well as whether its accurate or not, is up to the user.
